### 2016-07-01 finalText/theorBack.tex
Proposed Solution chapter almost done
Preliminary Thesis Version Completed

\begin{align}
    \mb{z}^{(t)} & = g(\mb{W}_z \mb{x}^{(t)} + \mb{R}_z \mb{y}^{(t-1)} + \mb{b}_z) \notag\\
    \mb{i}^{(t)} & = \sigma(\mb{W}_i \mb{x}^{(t)} + \mb{R}_i \mb{y}^{(t-1)} + \mb{p}_i \odot \mb{c}^{(t-1)} + \mb{b}_i) \notag\\
    \mb{f}^{(t)} & = \sigma(\mb{W}_f \mb{x}^{(t)} + \mb{R}_f \mb{y}^{(t-1)} + \mb{p}_f \odot \mb{c}^{(t-1)} + \mb{b}_f) \notag\\
    \mb{c}^{(t)} & = \mb{i}^{(t)} \odot \mb{z}^{(t)} + \mb{f}^{(t)} \odot \mb{c}^{(t-1)} \notag \\
    \mb{o}^{(t)} & = \sigma(\mb{W}_o \mb{x}^{(t)} + \mb{R}_o \mb{y}^{(t-1)} + \mb{p}_o \odot \mb{c}^{(t)} + \mb{b}_o) \notag\\
    \mb{c}^{(t)} & = \mb{o}^{(t)} \odot h(\mb{z}^{(t)}) \label{eq:equationsLSTM}
\end{align}
where $\odot$ is the Hadamard multiplication. The $i$-th element of the previous vectors in bold corresponds to the value of the gate of the $i$-th neuron of the layer, which is a very convenient and compact representation of the whole layer. Furthermore, if the layer has $N$ LSTM neurons and $M$ inputs (i.e. the size of the layer that precedes this), we see that the input weight matrices $\mb{W}_*$ and the  recurrent weight matrices $\mb{R}_*$ all have size $N \times M$, and that the bias weight matrices $\mb{b}_*$, the peephole weight matrices $\mb{p}_*$ and the matrices $\mb{z}^{(t)}$ through $\mb{c}^{(t)}$ have size $N \times 1$. Although useful for a high-level description in a programming language, the matrix representation  may not be suitable for a direct HDL port. In that case, in order to represent the operation of the $i$-\textit{single neuron}, all the above equations still hold, but instead of \textit{vectors} of outputs, we will have a single scalar output, and we only use the appropriate row in the weight matrices $\mb{W}_{*}$, $\mb{R}_{*}$ and the remaining.

@@

\section{Proposed Solution}\label{sec:propSol}
Given the previous discussion of how LSTM neurons work and their benefits when compared to other RNN architectures, this work aims to conceive and design an efficient dedicated FPGA implementation with on-chip learning that, surpasses the training/testing time of an equivalent CPU implementation in a general high-level language or of a framework (see Section~\ref{sec:wp_sh}).

As discussed in Chapter~\ref{chap:stateArt}, up to now there is only one FPGA implementation of LSTM cells~\cite{Chang15}, but there is no on-chip learning on the architecture (the weights are learned offline, and loaded in the FPGA before operation, and they are not changed while the FPGA system is operating), and my proposed work will implement an efficient LSTM implementation \emph{with} the ability to learn on-chip, which is an innovative and useful feature for the LSTM architecture on a dedicated hardware implementation. I will achieve that using the SPSA method described in~\ref{sec:training_lstm}, and inspired in the previous work of~\cite{Maeda05}.

This solution will combine the benefits of a dedicated hardware implementation, where the inherent parallelism so obviously visible in the network architecture can be fully exploited something that, predominantly, yields a much higher performance in terms of computation time than a naïve CPU implementation (as in~\cite{Maeda05} where a $21\times$ speed-up against an ARM CPU was acheived) with the flexibility that a reconfigurable platform such as an FPGA provides.

>>>>

\begin{align}
    \mb{z}^{(t)} & = g(\mb{W}_z \mb{x}^{(t)} + \mb{R}_z \mb{y}^{(t-1)} + \mb{b}_z) \notag\\
    \mb{i}^{(t)} & = \sigma(\mb{W}_i \mb{x}^{(t)} + \mb{R}_i \mb{y}^{(t-1)} + \mb{p}_i \odot \mb{c}^{(t-1)} + \mb{b}_i) \notag\\
    \mb{f}^{(t)} & = \sigma(\mb{W}_f \mb{x}^{(t)} + \mb{R}_f \mb{y}^{(t-1)} + \mb{p}_f \odot \mb{c}^{(t-1)} + \mb{b}_f) \notag\\
    \mb{o}^{(t)} & = \sigma(\mb{W}_o \mb{x}^{(t)} + \mb{R}_o \mb{y}^{(t-1)} + \mb{p}_o \odot \mb{c}^{(t)} + \mb{b}_o) \notag\\
    \mb{c}^{(t)} & = \mb{i}^{(t)} \odot \mb{z}^{(t)} + \mb{f}^{(t)} \odot \mb{c}^{(t-1)} \notag \\
    \mb{y}^{(t)} & = \mb{o}^{(t)} \odot h(\mb{z}^{(t)}) \label{eq:equationsLSTM}
\end{align}
where $\odot$ is the Hadamard multiplication. The $i$-th element of the previous vectors in bold corresponds to the value of the gate of the $i$-th neuron of the layer, which is a very convenient and compact representation of the whole layer. Furthermore, if the layer has $N$ LSTM neurons and $M$ inputs (i.e. the size of the layer that precedes this), we see that the input weight matrices $\mb{W}_*$ and the  recurrent weight matrices $\mb{R}_*$ all have size $N \times M$, and that the bias weight matrices $\mb{b}_*$, the peephole weight matrices $\mb{p}_*$ and the matrices $\mb{z}^{(t)}$ through $\mb{c}^{(t)}$ have size $N \times 1$. Although useful for a high-level description in a programming language, the matrix representation  may not be suitable for a direct HDL port. In that case, in order to represent the operation of the $i$-\textit{single neuron}, all the above equations still hold, but instead of \textit{vectors} of outputs, we will have a single scalar output, and we only use the appropriate row in the weight matrices $\mb{W}_{*}$, $\mb{R}_{*}$ and the remaining.

@@
